---
title: "R DiCITS packages downloads"
output: 
  html_document:
    toc: true
    toc_depth: 4
    number_sections: true
    fig_caption: true

---

```{r, include=FALSE, cache=FALSE}
load(file="/tmp/test_dicits.Rdata");

dat <- data.frame(dat);

rsnns_rows <- dat[dat$package == "RSNNS",]
frbs_rows <- dat[dat$package == "frbs",]
Rmalschains_rows <- dat[dat$package == "Rmalschains",]
RoughSets_rows <- dat[dat$package == "RoughSets",]
```



# RSNNS

Downloads from `r min(rsnns_rows$date)` to `r max(rsnns_rows$date)`: **`r nrow(rsnns_rows)`** unique downloads.

```{r, fig.width=10, fig.height=5, fig.cap = "Figure: RSNNS",   echo=FALSE}
aa <- data.frame(table(rsnns_rows$week));
plot(aa, xlab="Week", ylab="Downloads")
lines(aa)
```

# frbs

Downloads from `r min(frbs_rows$date)` to `r min(frbs_rows$date)` : **`r nrow(frbs_rows)`** unique downloads.

```{r, fig.width=10, fig.height=5, fig.cap = "Figure: frbs",   echo=FALSE}

aa <- data.frame(table(frbs_rows$week));
plot(aa, xlab="Week", ylab="Downloads")
lines(aa)
```

# Rmalschains

Downloads from `r min(Rmalschains_rows$date)` to `r min(Rmalschains_rows$date)`: **`r nrow(Rmalschains_rows)`** unique downloads.

```{r, fig.width=10, fig.height=5, fig.cap = "Figure: Rmalschains",   echo=FALSE}

aa <- data.frame(table(Rmalschains_rows$week));
plot(aa, xlab="Week", ylab="Downloads")
lines(aa)
```

# RoughSets

Downloads from `r min(RoughSets_rows$date)` to `r min(RoughSets_rows$date)`: **`r nrow(RoughSets_rows)`** unique downloads.


```{r, fig.width=10, fig.height=5, fig.cap = "Figure: RoughSets",   echo=FALSE}

aa <- data.frame(table(RoughSets_rows$week));
plot(aa, xlab="Week", ylab="Downloads")
lines(aa)
```


